---
title       : Developing Data Products
subtitle    : Course Project (Slidify) Pitch Presentation
author      : Wee Way Huay
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview
The prediction is for Miles per Gallon (MPG) based on the input of Gross Horsepower, No. of Cylinders and Weight entered by the users.

The ShinyApp has been deployed. Click <a href="https://wayhuay.shinyapps.io/Developing_Data_Products">here</a> to launch the App.

--- .class #id 

## Dataset
mtcars dataset is be used in the Miles per Gallon (MPG) prediction.
```{r}
data(mtcars)
head(mtcars, 5)
```

<h2>Source</h2>
Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

--- .class #id 

## Model
Linear model is used in this course project to predict the fuel efficiency of Miles per Gallon (MPG).
```{r}
Model <- lm(mpg ~ hp + cyl + wt, data=mtcars)

mpg <- function(hp, cyl, wt) {
  Model$coefficients[1] + Model$coefficients[2] * hp + 
    Model$coefficients[3] * cyl + Model$coefficients[4] * wt
}
```

--- .class #id 

## Graph Plots
```{r, echo=TRUE}
par(mfrow = c(2, 3))
plot(mtcars$hp, mtcars$mpg, main="MPG by Horsepower", xlab = "Horsepower"
     , ylab = "Miles Per Gallon (MPG)")
plot(mtcars$cyl, mtcars$mpg, main="MPG by Cylinders", xlab = "No. of Cylinder"
     , ylab = "Miles Per Gallon (MPG)")
plot(mtcars$wt, mtcars$mpg, main="MPG by Weight", xlab = "Weight"
     , ylab = "Miles Per Gallon (MPG)")
```
